BVP Paper

### 2017-11-17 tex/bvp_paper.tex
rough paper outline dumped in

\section{Introduction}
\label{sec:intro}

\section{Experiment} 
\label{sec:experiment}

\section{Results \& Discussion}
\label{sec:results}

>>>>

\section{Introduction}
\label{sec:intro}
Here we introduce why the timescale problem is hard, and how the choice of initial conditions
vastly effects the amount of time it takes for a solution to get to a meaningful solution

\section{Experiment} 
\label{sec:experiment}
Here we talk about how to set up the RB problem that we're going to solve, and exactly what
we're going to compare (how long the run is going to go from base and from bvp, how much time
we're going to compare over after that, etc.)  We need to compare over a short enough timescale
that the effects of BVPs don't get washed away, and we also need to compare over long enough
timescales that we get the rare events we expect.  This is where we put a figure showing the
time evolution of energy in IVP / BVP side-by-side.

\section{Results \& Discussion}
\label{sec:results}
Here we talk about how the solutions are different, or similar.  This includes:
\begin{enumerate}
\item Showing that the flow fields look similar
\item Showing how the temperature / flux profiles look similar/different
\item showing how Nu and Re scale with Ra in BVP / IVP.
\item showing how the PDFs of $w$, $wT$, and $T$ change.
\end{enumerate}

Then we need to make some comments about whether this is good or bad

Then we need to mention how the same thing can be done in stratified, just there you don't
assume symmetrical boundary layers.
